
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Développement d'une plateforme E-learning}

\author{Asma Ben Ayech}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Licence en ingénieurie des systémes informatiques}
\speciality{IOT}

%% Encadrant professionnel
\proFramerName{Ouertani Abderahim}


%% Encadrant académique
\academicFramerName{Amdouni Asma}


%% Entreprise d'accueil
\companyName{Inno-Think}

%% Année universitaire
\collegeYear{2023 - 2024}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J'autorise l'étudiant à faire de son rapport de stage en vue d'une soutenance.}

\academicSignSentence{J'autorise l'étudiant à faire de son rapport de stage en vue d'une soutenance.}

%%% AR
\arabicAbstract{تم إنجاز هذا العمل داخل شركة اكتيا من أجل التحقق من صحة التدريب الإلزامي للحصول على الدبلوم الوطني للترخيص في العلوم التطبيقية والتكنولوجيا.
يتكون المشروع من تصميم تطبيق ويب باستخدام Visual Studio Code كبيئة تطوير.
الهدف من منصتي هو اكتشاف جميع أنواع البيانات المسربة في الويب المظلم والإبلاغ عن النتائج.}



%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{Ce travail a été réalisé au sein de l'entreprise ACTIA ES afin de valider le stage obligatoire pour l'obtention du Diplôme National de Licence en Sciences Appliquées et Technologie.
Le projet consiste à concevoir une application web utilisant Visual Studio Code comme environnement de développement.
L'objectif de ma plateforme est de détecter toutes sortes de fuites de données dans le Dark Web et de rapporter les résultats.}


%%% EN
\englishAbstract{This work was realized within the company ACTIA ES in order to validate the compulsory internship for the obtaining of the National Diploma of License in Applied Sciences and Technology. 
The project consists of designing a web application using Visual Studio Code as development environment. 
The objective of my platform is to Detect all kinds of leaked data in the Dark Web and to report the results.}



%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{false}

